null_model

### 2020-09-14 analysis/ts_null_model.Rmd
parallel FD using new settings

get_parallel_FD <- function(group_num){
  browser()
  group_plots <- plot_sizes %>% filter(group == group_num)
  group_data <- sample_occurrence %>% filter(plot_id %in% group_plots$plot_id)

  future::plan(multiprocess)
  fd <- map_dfr(group_plots$plot_id[1:3], get_plot_FD, 
                   traits = group_trait_data, occ_df = group_data)
    #future_map(group_plots$plot_id, get_fd_safe, data = group_data)

>>>>

get_parallel_FD <- function(group_num){
  group_plots <- plot_sizes %>% filter(group == group_num)
  group_data <- sample_occurrence %>% filter(plot_id %in% group_plots$plot_id)
  group_trait_data <- trait_data %>% filter(id %in% colnames(group_data)[-(1:3)])

  future::plan(multiprocess)
  fd <- map_dfr(group_plots$plot_id[1:3], get_plot_FD,
                traits = group_trait_data, occ_df = group_data,
                m = "min", corr = "cailliez")
    #future_map(group_plots$plot_id, get_fd_safe, data = group_data)
